|

### 2024-10-25 output/seminar-slideshow.qmd
Embed graphical configuration in slideshow file
Avoid dependency (in principle) from the graphical representation example for the paper

# Graphical configuration options:
loadfonts(device = "win") # Load fonts (if necessary)
par(family = "Arial", adj = 0.5) # Set graphical device params

margins <- c(12, 1.3, 8, 1.3) # margins for the sem path plots
```

```{r color-palettes}
PALETTE_UNED <- c(
  normal = "#00533e",
  medium = "#427562",
  light  = "#86a699",
  white  = "#cddad5"
)
PALETTE_APPLE <- c(
  normal = "#749f4c",
  medium = "#8aac5d",
  light  = "#a2bc7e",
  white  = "#cddbb8"
)
PALETTE_BLUE <- c(
  normal = "#5c6eb1",
  medium = "#7683bd",
  light  = "#929acb",
  white  = "#d4d6eb"
)
PALETTE_TANGERINE <- c(
  normal = "#d76f47",
  medium = "#dd8964",
  light  = "#e4a482",
  white  = "#f0cfb9"
)
PALETTE_STRAWBERRY <- c(
  normal = "#da5268",
  medium = "#c87384",
  light  = "#daa6b1",
  white  = "#efdbdf"
)
PALETTE_RASPBERRY <- c(
  normal = "#90214a",
  medium = "#8e4d60",
  light  = "#af848b",
  white  = "#dac7c7"
)
```

```{r read-chunks}
#| cache: false
read_chunk("src/Graphical_example_paper.R")
```

```{r sources, cache=FALSE}
```

```{r constants, cache=FALSE}
```

```{r replace-plot-params}
GRAPH_FONT   <- "Arial"    # Replace default font to comply with UNED identity
FONT_SIZE    <- 24         # Replace default font size for slideshow
AXIS_LAB_POS <-   .5       # Replace default axis label position for slideshow
LINE_WIDTH   <-   .75      # Replace default line width for slideshow
AXIS_COLOR   <- "darkgray" # Replace default grid line color for slideshow
```

```{r graphical-output-conf, cache=FALSE}
```

@@

simple_spec      |>
  semPlotModel() |>
  semPaths(
    border.color = c(
      item_colors,       # Item colors
      F1_COLOR, F2_COLOR # Factor colors
    ),
    edge.color   = c(
      item_colors, # Loading colors
      "black"      # Correlation color
    ),
    residuals    = FALSE,
    thresholds   = FALSE,
    intercepts   = FALSE,
    fixedStyle   = 1,
    curve        = 3,
    label.cex    = 1.6,
    sizeMan      = 10,
    sizeLat      = 14,
    border.width = 3,
    edge.width   = 3,
    mar          = margins
  )
```
:::

@@

complex_spec     |>
  semPlotModel() |>
  semPaths(
    border.color = c(
      item_colors,       # Item colors
      F1_COLOR, F2_COLOR # Factor colors
    ),
    edge.color   = c(
      edge_colors, # Loading colors
      "black"      # Correlation color
    ),
    residuals    = FALSE,
    thresholds   = FALSE,
    intercepts   = FALSE,
    fixedStyle   = 1,
    curve        = 3,
    label.cex    = 1.6,
    sizeMan      = 10,
    sizeLat      = 14,
    border.width = 3,
    edge.width   = 3,
    mar          = margins
  )
```
:::

@@

method_spec      |>
  semPlotModel() |>
  semPaths(
    border.color = c(
      F1_COLOR |> rep(6), # Item colors
      F1_COLOR, F2_COLOR  # Factor colors
    ),
    edge.color   = edge_colors, # Loading colors
    residuals    = FALSE,
    thresholds   = FALSE,
    intercepts   = FALSE,
    fixedStyle   = 1,
    curve        = 3,
    label.cex    = 1.6,
    sizeMan      = 10,
    sizeLat      = 14,
    border.width = 3,
    edge.width   = 3,
    mar          = margins
  )
```
:::

>>>>

# Graphical configuration options:
loadfonts(device = "win") # Load fonts (if necessary)
par(family = "Arial", adj = 0.5) # Set graphical device params
```

```{r sources}
source("R/LaTeX_math.R", encoding = 'UTF-8')
source("R/Output.R",     encoding = 'UTF-8')
```

```{r color-palettes}
MARGINS <- c(12, 1.3, 8, 1.3) # margins for the sem path plots

PALETTE_UNED <- c(
  normal = "#00533e",
  medium = "#427562",
  light  = "#86a699",
  white  = "#cddad5"
)
PALETTE_APPLE <- c(
  normal = "#749f4c",
  medium = "#8aac5d",
  light  = "#a2bc7e",
  white  = "#cddbb8"
)
PALETTE_BLUE <- c(
  normal = "#5c6eb1",
  medium = "#7683bd",
  light  = "#929acb",
  white  = "#d4d6eb"
)
PALETTE_TANGERINE <- c(
  normal = "#d76f47",
  medium = "#dd8964",
  light  = "#e4a482",
  white  = "#f0cfb9"
)
PALETTE_STRAWBERRY <- c(
  normal = "#da5268",
  medium = "#c87384",
  light  = "#daa6b1",
  white  = "#efdbdf"
)
PALETTE_RASPBERRY <- c(
  normal = "#90214a",
  medium = "#8e4d60",
  light  = "#af848b",
  white  = "#dac7c7"
)

GRAPH_FONT   <- "Arial"    # Replace default font to comply with UNED identity
FONT_SIZE    <- 24         # Replace default font size for slideshow
AXIS_LAB_POS <-   .5       # Replace default axis label position for slideshow
LINE_WIDTH   <-   .75      # Replace default line width for slideshow
AXIS_COLOR   <- "darkgray" # Replace default grid line color for slideshow
```

```{r graphical-output-conf}
theme_set( # `ggplot` output configuration
  theme_classic(
    base_size      = FONT_SIZE,
    base_family    = GRAPH_FONT,
    base_line_size = LINE_WIDTH
  ) %+replace%
    theme(
      axis.title.x = element_text(hjust = AXIS_LAB_POS),
      axis.title.y = element_text(vjust = AXIS_LAB_POS, angle = 0),
      panel.grid   = element_line(color = AXIS_COLOR)
    )
)
```

@@

simple_spec      |>
  semPlotModel() |>
  semPaths(
    border.color = c(
      item_colors,       # Item colors
      F1_COLOR, F2_COLOR # Factor colors
    ),
    edge.color   = c(
      item_colors, # Loading colors
      "black"      # Correlation color
    ),
    residuals    = FALSE,
    thresholds   = FALSE,
    intercepts   = FALSE,
    fixedStyle   = 1,
    curve        = 3,
    label.cex    = 1.6,
    sizeMan      = 10,
    sizeLat      = 14,
    border.width = 3,
    edge.width   = 3,
    mar          = MARGINS
  )
```
:::

@@

complex_spec     |>
  semPlotModel() |>
  semPaths(
    border.color = c(
      item_colors,       # Item colors
      F1_COLOR, F2_COLOR # Factor colors
    ),
    edge.color   = c(
      edge_colors, # Loading colors
      "black"      # Correlation color
    ),
    residuals    = FALSE,
    thresholds   = FALSE,
    intercepts   = FALSE,
    fixedStyle   = 1,
    curve        = 3,
    label.cex    = 1.6,
    sizeMan      = 10,
    sizeLat      = 14,
    border.width = 3,
    edge.width   = 3,
    mar          = MARGINS
  )
```
:::

@@

method_spec      |>
  semPlotModel() |>
  semPaths(
    border.color = c(
      F1_COLOR |> rep(6), # Item colors
      F1_COLOR, F2_COLOR  # Factor colors
    ),
    edge.color   = edge_colors, # Loading colors
    residuals    = FALSE,
    thresholds   = FALSE,
    intercepts   = FALSE,
    fixedStyle   = 1,
    curve        = 3,
    label.cex    = 1.6,
    sizeMan      = 10,
    sizeLat      = 14,
    border.width = 3,
    edge.width   = 3,
    mar          = MARGINS
  )
```
:::
